CS246: Twitter Purification

### 2014-06-08 Paper.tex
Added ShiWen's stuff

TODO: Shi Wen

@@

TODO: Shi Wen
\subsubsection*{Letter similarity: Viterbi}
\paragraph{} Several hundred correction candidates may be found for a word, based on searching within a particular edit distance or the same Soundex/Metaphone class. To trim this list, we first make some intuitive assumptions about the manner in which Twitter users typically misspell their words.
\begin{itemize}
\item Abbreviation: Twitter words are usually shorter than their correct counterparts
\item Letter similarity: the same important letters are usually present in the Twitter word as the correct counterpart. There are a few phonetic exceptions to this, e.g. substituting \textit{d} for \textit{th}, as in \textit{dere} vs \textit{there}.
\item Transposition of remaining significant letters is rare, which makes sense if other letters have already been omitted for brevity.
\end{itemize}
With these observations in mind, we set out to find a reasonable scoring algorithm to measure the similarity between a Twitter word versus its correction candidate.

@@

\\
TODO: Zijun or Shiwen to add some data about comparison with existing spell checker

@@

>>>>

\paragraph{} A phonetic algorithm is an algorithm for indexing of words by their pronunciation. The goal is for homophones to be encoded to the same representation so that they can be matched despite minor differences in spelling. We assume that words with the same or similar phonetic representations are more likely to be confounded with one another. There are many complex algorithms to create phonetic mappings. Among the best known phonetic algorithms are: Soundex, Daitch-Mokotoff Soundex, Kolner Phonetik, Metaphone, Double Metaphone, New York State Identification and Intelligence System, Match Rating Approach, etc. In this paper, we use Soundex and Double Metaphone algorithms for generating a phonetic candidate list for each misspelled word.
\paragraph{} Soundex is the most widely known algorithm of all phonetic algorithms. The algorithm mainly encodes consonants; a vowel will not be encoded unless it is the first letter.The Soundex code for a name consists of one letter followed by three numerical digits: the letter is the first letter of the name, and the digits encode the remaining consonants.The specific algorithm can be checked here\footnote{\href{http://www.sound-ex.com/soundex_method.htm}{soundex algorithm}}.
\paragraph{} In this project, we indexed each of the words in the 800,000 tweets to its phonetic index and create an inverted phonetic dictionary that maps each phonetic representation to a list of words that shares the same phonetic representation. For example, \textit{people} is mapped to p140; from the inverted phonetic map (p140), we obtain the word list [\textit{peaple, peopleeee,  piebbal, people, peple, pupil, puffle, peoople, peoplle, pueblo, phaphela, pahabol, people, people, payable, paypal, peopleee, pablooo, papell, poeple, poweful, peopl, papal, pablo, pavel, peoiple, peoplee, people, pebble}]. We did not exclude candidates based on the dictionary to allow for the presence of slang and other appropriate words that do not exist in the dictionary.

@@

\paragraph{} The Metaphone algorithm fundamentally improves upon the Soundex algorithm by using information about variations and inconsistencies in English spelling and pronunciation to produce a more accurate encoding. The Double Metaphone phonetic encoding algorithm is the second generation of this algorithm, where `double' refers to a primary and a secondary encoding for a string. For example, encoding the name \textit{Schmidt} yields a primary code of \textit{XMT} and a secondary code of \textit{SMT}, and \textit{Smith}  yields [\textit{SM0, XMT}] -- both have XMT in common. See Appendix A-5 for an example of a candidate pool derived for \textit{ppl}.

\paragraph{} In our project, we combine and compress the inverted soundex phonetic list and inverted double\_metaphone phonetic list and use that as the final phonetic candidate list for each single word in tweets.
\subsubsection*{Letter similarity: Viterbi}
\paragraph{} Several hundred correction candidates may be found for a word, based on searching within a particular edit distance or the same Soundex/Metaphone class. To trim this list, we first make some intuitive assumptions about the manner in which Twitter users typically misspell their words.
\begin{itemize}
\item Abbreviation: Twitter words are usually shorter than their correct counterparts
\item Letter similarity: the same important letters are usually present in the Twitter word as the correct counterpart. There are a few phonetic exceptions to this, e.g. substituting \textit{d} for \textit{th}, as in \textit{dere} vs \textit{there}.
\item Transposition of remaining significant letters is rare, which makes sense if other letters have already been omitted for brevity.
\end{itemize}
With these observations in mind, we set out to find a reasonable scoring algorithm to measure the similarity between a Twitter word versus its correction candidate.

@@

\paragraph{}We compared the results with Aspell's algorithm\footnote{\href{http://aspell.net/}{Aspell}}, which also returns a candidate list for each single input word. The results showed that the Aspell algorithm produced 303/368 errors, which is much higher than our Twitter purification algorithm. We surmise that the main reasons for the Aspell's poor performance is due to the nature of malformed Twitter data, and Aspell's harder constraints on using its dictionary.

@@

\subsection*{A-5 Double Metaphone}
\begin{lstlisting}
Double Metaphone Dict(`people'): [`PPL', `']
Inverted Metaphone Dict(`PPL') = [peaple, buble, babble, peoplle, pablooo, pupil, pppl, people, papell, pebble, peopleeee, pueblo, peoople, payable, poeple, bubbly, bubble, peoiple, bible, bpl, bubbaloo, piebbal, peopl, peopleee, people, bypoll, pablo, bhopal, papal, paypal, peoplee, bobble, peple]
\end{lstlisting}
